animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2024-02-23 animbook-journal.Rmd
spell checked

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
abstract: >
  Performance is often reported in quantiles or ranks and often repeatedly provided over time. Between elections, voters often switch party preferences, which produces categorical values over time. Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called \CRANpkg{animbook}. Functions to pre-process the data and prepare it for the animation are provided. The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address: 
      - Department of Econometrics and Business Statistics
      - Melbourne, Australia
    email: dicook@monash.edu
    orcid: 0000-0002-3813-7155
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib
---

@@

The interactive chart featured in the New York Times article (Figure \@ref(fig:nyt)) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to the @race. This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.

  In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group. This dynamic visualization constructs questions on the broader use of this visualization to other types of data. The potential use of this visualization on accounting data is to convey a message, as reported by the @oecd_report, that the concept of zombie companies is not unique to Japan alone. It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.

@@

  This animation was developed using the software based on JavaScript, D3.js (@d3js), and WebGL (@webgl). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.

@@

In the data structure, there are requirements that must be followed for reproducing the animation. First, the data set needs to be in the `tidy data` format (@tidy-data). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered.

@@

  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. The \CRANpkg{gganimate} includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.

@@

  In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in media applications provided in their systems. As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized. The `nframes` dictates the number of frames to be rendered, while `fps` controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

@@

  The argument for the `anim_prep()` and `anim_prep_cat()` function are listed in the Table `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively. The `data`, `id`, `values`, and `time` arguments are required for both functions.

@@

  The names of these plots draw inspiration from native Australian animals. The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo. The final plot is named after the Funnel Web Spider, drawing parallels between the plot's features and the distinctive legs of the spider.

@@

In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five grey bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018. Points represent individual companies with color indicating the country of registration. Points that stay within the bar indicate companies that remain in the same quartile over the entire time period. If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot. Note that all the companies in the "Not listed" category were listed at some point during this time period. It can be seen that most companies stay in the same quantile group over the time period. There are several companies that move up and down, and most of these are US companies. This supports the @oecd_report claim that US companies have a higher turnover rate compared to Japanese companies.

@@

  In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The grey regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category. All the companies in the Top 25% were US companies. Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25% in 2006. It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

>>>>

---
title: "animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation"
abstract: >
  Performance is often reported in quantiles or ranks and often repeatedly provided over time. Between elections, voters often switch party preferences, which produces categorical values over time. Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," we provide new visualization functions to generate animations that display this type of data in an R package called animbook. Functions to pre-process the data and prepare it for the animation are provided. The methods will be suitable generally for data where categorical variables are measured over time, and provide a way to engagingly view changes.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address: 
      - Department of Econometrics and Business Statistics
      - Melbourne, Australia
    email: dicook@monash.edu
    orcid: 0000-0002-3813-7155
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib
---

@@

The interactive chart featured in the New York Times article (Figure \@ref(fig:nyt)) unveils the issue of income disparities between black and white children who were raised in families with comparable income according to @race. This visualization reveals that, compared to white children, black children are more likely to drop down to the lower-income group, given that they both grew up in wealthy families.

  In the visualization, each observation is initially classified into one group at the start and potentially transitions into either the same group or a different group. This dynamic visualization constructs questions on the broader use of this visualization to other types of data. The potential use of this visualization on accounting data is to convey a message, as reported by @oecd_report, that the concept of zombie companies is not unique to Japan alone. It is also present in the United States, which has a faster metabolization rate (more new listings and exits) relative to Japan.

@@

  This animation was developed using software based on JavaScript, D3.js (@d3js), and WebGL (@webgl). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins.

@@

In the data structure, there are requirements that must be followed for reproducing the animation. First, the data set needs to be in a `tidy data` format (@tidy-data). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered.

@@

  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. The \CRANpkg{gganimate} includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.

@@

  In \CRANpkg{gganimate}, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in media applications provided in their systems. As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized. The `nframes` dictate the number of frames to be rendered, while `fps` controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

@@

  The arguments for the `anim_prep()` and `anim_prep_cat()` functions are listed in Tables `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively. The `data`, `id`, `values`, and `time` arguments are required for both functions.

@@

  The names of these plots draw inspiration from native Australian animals. The comprehensive plot is named Kangaroo, while its subset is referred to as Wallaby, representing a smaller version of the Kangaroo. The final plot is named after the Funnel Web Spider, drawing inspiration from the plot's features and the distinctive legs of the spider.

@@

In the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`) the five gray bars indicate the five categories (Top 25%, 25-50, 50-75, 75-100, Not listed) across years 2006 and 2018. Points represent individual companies with color indicating the country of registration. Points that stay within the bar indicate companies that remain in the same quartile over the entire time period. If a company drops in performance or improves performance to the extent of switching quartile, the corresponding point will jump up or down in this plot. Note that all the companies in the "Not listed" category were listed at some point during this time period. It can be seen that most companies stay in the same quantile group over the time period. There are several companies that move up and down, and most of these are US companies. This supports the @oecd_report claim that US companies have a higher turnover rate compared to Japanese companies.

@@

  In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category. All the companies in the Top 25% were US companies. Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25% in 2006. It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.
